Nested Stochastic Block Models Applied to the Analysis of Single Cell Data

### 2021-07-16 manuscript.tex
use eps from now on
Fig 1 eps
I make my own pictures now,from source...
Another PDF figure

\begin{figure}[H]
\centering
\includegraphics[keepaspectratio,width=0.6\textwidth,height=\textheight]{FIgure_Random.png}
\caption[]{Modeling randomised data. (A) UMAP embedding of ~3k PBMC after standard processing with Leiden approach (left) or nSBM (right). Cell grouping is consistent for both the approaches (Adjusted Rand Index $ARI=0.869$). (B) UMAP embedding of the same data after randomisation of \emph{k}NN graph edges. In this case nSBM does not return any cell grouping, while optimisation of modularity finds up to 24 different cell groups}\label{FigureRandom}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[keepaspectratio,width=0.6\textwidth,height=\textheight]{FigureTian.pdf}
\caption[]{Analysis of a mixture of 5 known cell lines. (A) UMAP embedding coloured and labeled by cell line identity. H1975 cells (orange) show two distinct groups reflecting an internal heterogeneity. (B) UMAP embedding showing cells coloured by level 1 of the hierarchy proposed by the nested Stochastic Block Model. (C) UMAP embedding showing cells coloured according to the Leiden method at resolution $\gamma = 1$. (D) UMAP embedding coloured by the classification made by SCCAF when partitions in (B) are used. (E) UMAP embedding coloured by the classification made by SCCAF when partitions in (C) are used.}\label{FigureTian}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[keepaspectratio,width=\textwidth,height=0.55\textheight]{Figure_Visium_Spatial.png}
\caption[]{Analysis of spatial transcriptomics of a coronal section of mouse brain by Visium H\&E. In the first panel, original tissue annotation is given. Tissues are well defined at default resolution for the standard approach. When resolution is decreased to $\gamma = 0.5$, cells from the dentate gyrus are merged to the hippocampus. When nSBM is used, the structure of the pyramidal is maintained at different levels of the hierarchy}\label{Figure_Visium}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[keepaspectratio,width=0.6\textwidth,height=\textheight]{Figure_Hemato_Lineage.png}
\caption[]{Analysis of hematopoietic differentiation. Each panel presents a low dimensional embedding of single cells next to a radial tree representation of the nSBM hierarchy. Cells are coloured according to groupings at level 2 of the hierarchy, group 0 marks the most primitive population (A). In subsequent panels, cells are coloured using a signature of Erythroid lineage (B), Monocytes (C) or Neutrophils (D).}\label{Figure_Hemato_Lineage}
\end{figure}

>>>>

\begin{figure}[H]
\centering
\includegraphics[keepaspectratio,width=0.5\textwidth,height=\textheight]{FIgure_Random.pdf}
\caption[]{Modeling randomised data. (A) UMAP embedding of ~3k PBMC after standard processing with Leiden approach (left) or nSBM (right). Cell grouping is consistent for both the approaches (Adjusted Rand Index $ARI=0.869$). (B) UMAP embedding of the same data after randomisation of \emph{k}NN graph edges. In this case nSBM does not return any cell grouping, while optimisation of modularity finds up to 24 different cell groups}\label{FigureRandom}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[keepaspectratio,width=1\textwidth,height=\textheight]{FigureTian.pdf}
\caption[]{Analysis of a mixture of 5 known cell lines. (A) UMAP embedding coloured and labeled by cell line identity. H1975 cells (orange) show two distinct groups reflecting an internal heterogeneity. (B) UMAP embedding showing cells coloured by level 1 of the hierarchy proposed by the nested Stochastic Block Model. (C) UMAP embedding showing cells coloured according to the Leiden method at resolution $\gamma = 1$. (D) UMAP embedding coloured by the classification made by SCCAF when partitions in (B) are used. (E) UMAP embedding coloured by the classification made by SCCAF when partitions in (C) are used.}\label{FigureTian}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[keepaspectratio,width=0.6\textwidth,height=\textheight]{Figure_Visium_Spatial.pdf}
\caption[]{Analysis of spatial transcriptomics of a coronal section of mouse brain by Visium H\&E. In the first panel, original tissue annotation is given. Tissues are well defined at default resolution for the standard approach. When resolution is decreased to $\gamma = 0.5$, cells from the dentate gyrus are merged to the hippocampus. When nSBM is used, the structure of the pyramidal is maintained at different levels of the hierarchy}\label{Figure_Visium}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[keepaspectratio,width=1\textwidth,height=\textheight]{Figure_Hemato_Lineage.pdf}
\caption[]{Analysis of hematopoietic differentiation. Each panel presents a low dimensional embedding of single cells next to a radial tree representation of the nSBM hierarchy. Cells are coloured according to groupings at level 2 of the hierarchy, group 0 marks the most primitive population (A). In subsequent panels, cells are coloured using a signature of Erythroid lineage (B), Monocytes (C) or Neutrophils (D).}\label{Figure_Hemato_Lineage}
\end{figure}
